---
title: "Weight of Fish"
author: "Annabelle Polack"
date: "6/30/22`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
fish<-read.csv(file="Fish.csv")
```



# Predicting Fish Weight
I predict that most of the fish will be in the triple digits around the 100s or higher.

## Perch
```{r}
Perch<-filter(fish, Species=="Perch")
Perch<- select(Perch, -Species)
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



### Best Two regressor model
The best regression model is the one with the highest adjusted r squared value and that is Height and Width and it has 2 regressors, so it is the model we're looking for.

## Pike
```{r}
Pike<-filter(fish, Species=="Pike")
Pike<- select(Pike, -Species)
```


### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Two regressor model
The best model is Length 1 and Length 2, because it has 2 regressors, so this is the model we're looking for.

## Roach
```{r}
Roach<-filter(fish, Species=="Roach")
Roach<- select(Roach, -Species)
```


### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Two regressor model
The best model is the one with Length 3 and Width because it has 2 regressors, so this is the model we're looking for.


## Final Summary Statements
Looking through all the data, we can see that the Perch fish had a high R squared value which was Height and Width. The Pike fish had a high R squared value which was length 1 and length 2. The final fish which was the Roach had a high R squared value which was length 3 and width. All of them contained two regressors which were the second highest values. 
